A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/intro.tex
More changes to the introduction

This paper describes the planning component for a robotic system that
continuously deliberates in a stochastic dynamic environment in order
to achieve objectives set by the user, and acquire knowledge about its
surroundings. This domain features partial observability, particularly
because the state is not perfectly known, and state information is
gained by the robot through the use of unreliable sensing
actions. Using a propositionally factored state representation, for
interesting tasks the corresponding POMDP model is too large for a
POMDP solver to be applied directly. Inspired by the replanning
approaches used successfully for MDP
planning~\cite{yoon:etal:2007,yoon:etal:2008}, we propose an approach
that uses a replanning system to compute a reasonably valuable trace
in the model, and then uses a decision-theoretic planner on small
subproblems where reasoning about observations might be useful. We
refer to the complete system as a {\em switching continual
planner}. The approach is not optimal, particularly as it is based on
a satisficing sequential planner, but it performs better than the
sequential planner alone, and is fast enough to be used in real-time
on a mobile robot for decision-making.

@@

Our switching system is domain independent, taking domain and problem
descriptions in a first-order declarative language we have developed,
called the decision-theoretic planning domain definition language
(DTPDDL). From those descriptions of POMDP, we automatically construct
a deterministic model for the sequential planner, that includes
operators which correspond to assumptions about the values of
imperfectly known state variables. Assumptions scheduled by the
sequential system are used to propose a pragmatic abstract
belief-state space to the decision-theoretic system, and to modify the
reward function for the decision-theoretic planner, so that it might
pursue sensing related to those assumptions.

@@

The sequential planner we use is based
on \fastdownward \cite{fast-downward}. We add the capability to
replan, and also allow agent knowledge to be represented explicitly,
so we can write actions that gain the agent knowledge. LEASE CITE
MICHAEL's WORK AS THE BASIS FOR THIS. For the decision-theoretic
planner we have implemented our own forward search in the belief-state
space.

>>>>

This paper describes the planning component for a robotic system that
continuously deliberates in a stochastic dynamic environment in order
to achieve objectives set by the user, and acquire knowledge about its
surroundings. This domain features partial observability, particularly
because the state is not perfectly known, and state information is
gained by the robot through the use of unreliable sensing
actions. Using a propositionally factored state representation, for
interesting tasks the corresponding POMDP model is too large for a
POMDP solver to be applied directly. Inspired by the replanning
approaches used successfully for MDP
planning~\cite{yoon:etal:2007,yoon:etal:2008}, we propose a continual
planning approach that uses a classical planning system to compute a
reasonably valuable trace in the model, and then uses a
decision-theoretic planner on small subproblems where reasoning about
observations might be useful. We refer to the complete system as a
{\em switching continual planner}. The approach is not optimal,
particularly as it relies on the results of sequential planning
directly. It does nevertheless perform better than a purely sequential
replanner, and is fast enough to be used for real-time decision-making
on a mobile robot.

@@

Our switching system is domain independent, taking domain and problem
descriptions in a first-order declarative language we have developed,
called the decision-theoretic planning domain definition language
(DTPDDL). From those descriptions of POMDPs, we automatically
construct a deterministic model for the sequential planner. That model
includes operators which correspond to assumptions about the values of
imperfectly known state variables. Assumptions scheduled by the
sequential system are used to propose a pragmatic abstract
belief-state space to the decision-theoretic system, and to modify the
reward function, so that system might pursue sensing related to those
assumptions.

@@

%% The sequential planner we use is based
%% on \fastdownward~\cite{fast-downward}. We add the capability to replan
%% ~\cite{brenner:nebel:jaamas09}, and also allow agent
%% knowledge to be represented explicitly, so we can write actions that
%% gain the agent knowledge. LEASE CITE MICHAEL's WORK AS THE BASIS FOR
%% THIS. For the decision-theoretic planner we have implemented our own
%% forward search in the belief-state space.
